Music Versus No Music Effectiveness On Cognitive Response Time and Typing Efficiency

### 2024-05-07 Latex Source/paper.tex

The study done through Kiss and Linnell~\cite{kiss2021effect} saw opposite results as to Gonzalez and Aiello~\cite{Gonzalez_Aiello_2019}. The music or background noise ``enhanced'' the reaction time and performance of the tasks that are given to be completed. 
The results from Mathew~\cite{mathew2022inherently} were split. 
The music was a detriment for logic puzzles in the user's accuracy but aided in the efficiency of a writing task. 
According to Bramwell-Dicks et al., the instrumental music used in their study had better results on typists in speed and accuracy whereas music with vocals, the participants fared worse~\cite{bramwell2016can}.
While only a quasi-experiment, Oldham et al., found that personal headphones and Walkmans for employees had a positive correlation if the job complexity was not complex but also that employee satisfaction at this company was higher if they were allowed to use their walkman while working~\cite{oldhamListen}. Dobbs et al., also found the correlation that while music produced lower scores than silence it was better than just ``noise''~\cite{effectsOfBackgroundDobbs}.
Further research by \cite{gupta2023effect}Gupta et al. (2023) explored the effects of different music genres on attention and memory during cognitive tasks, providing valuable insights into how musical characteristics influence cognitive performance. Similarly, Sharma et al. \cite{sharma2022impact}(2022) conducted a study examining the impact of various types of music on productivity and task performance, shedding light on the differential effects of instrumental and lyrical music on cognitive function.

\subsection{Eye Tracking}
In addition to the aforementioned studies, an innovative approach to eye-tracking technology was presented by \cite{Malaikar2018Arduino}Malaikar et al. (2018) in their work titled "Arduino Based Eye-Writer Using PS3 Eye Camera." This research introduced an eye-tracking device and custom software, known as the Eye-Writer, which aimed to aid individuals with neuromuscular disorders and injuries in drawing or writing using only their eye movements. The Eye-Writer utilized an Arduino platform and a PS3 Eye Camera to track the movement of the user's eyes, enabling creative expression without the need for physical mobility. This novel application of eye-tracking technology showcases the diverse range of potential applications in assistive technology and human-computer interaction.

@@

\section{Conclusion and Future Works}
In conclusion, our study investigated the influence of auditory stimuli on eye movements using an eyetracking device. While the typing test results were not statistically significant, our analysis of the heatmap data revealed intriguing patterns in participants' eye movements under different auditory conditions. Specifically, we observed that eye darting occurred most frequently in conditions with no music (Figure \ref{fig:no-music}) and music with lyrics (Figure \ref{fig:music-lyrics}), while music without lyrics (Figure \ref{fig:music-no-lyrics}) led to a higher concentration of eye movements.
Looking ahead, there are several avenues for future research and improvements. Firstly, it would be beneficial to incorporate a recording of the specific typing test completed by each participant, as we suspect that familiarity with certain song lyrics may have influenced typing performance. Additionally, expanding the length and diversity of text in the typing test could provide further insights into how different stimuli affect typing accuracy and speed. Experimenting with a broader range of auditory stimuli, including older songs or entirely different texts, could help elucidate the factors influencing participants' eye movements.
Furthermore, exploring the cognitive mechanisms underlying the observed eye movement patterns and their relationship with auditory processing could enhance our understanding of multimodal perception and attention. Investigating individual differences in response to auditory stimuli, such as musical preferences or language proficiency, could also offer valuable insights into the variability of eye movement behavior across diverse populations.
In summary, our findings contribute to the growing body of research on the interplay between auditory stimuli and visual attention, highlighting the need for continued exploration and refinement of experimental methodologies to uncover the underlying mechanisms. By addressing these avenues for future research, we can further advance our understanding of human perception and enhance the design of technologies aimed at optimizing cognitive performance in various contexts.

\begin{figure}
    \centering
    \includegraphics[width=0.5\linewidth]{1.png}
    \caption{Music with no Lyrics}
    \label{fig:enter-label}
\end{figure}
\begin{figure}
    \centering
    \includegraphics[width=0.5\linewidth]{Music with Lyrics.png}
    \caption{Music with Lyrics}
    \label{fig:enter-label}
\end{figure}
\begin{figure}
    \centering
    \includegraphics[width=0.5\linewidth]{3.png}
    \caption{No Music}
    \label{fig:enter-label}
\end{figure}

>>>>

The study done through Kiss and Linnell~\cite{kiss2021effect} saw opposite results as to Gonzalez and Aiello~\cite{Gonzalez_Aiello_2019}. The music or background noise ``enhanced'' the reaction time and performance of the tasks that are given to be completed. 
The results from Mathew~\cite{mathew2022inherently} were split. 
The music was a detriment for logic puzzles in the user's accuracy but aided in the efficiency of a writing task. 
According to Bramwell-Dicks et al., the instrumental music used in their study had better results on typists in speed and accuracy whereas music with vocals, the participants fared worse~\cite{bramwell2016can}.
While only a quasi-experiment, Oldham et al., found that personal headphones and Walkmans for employees had a positive correlation if the job complexity was not complex but also that employee satisfaction at this company was higher if they were allowed to use their walkman while working~\cite{oldhamListen}. Dobbs et al., also found the correlation that while music produced lower scores than silence it was better than just ``noise''~\cite{effectsOfBackgroundDobbs}.
Further research by~\cite{gupta2023effect}Gupta et al. (2023) explored the effects of different music genres on attention and memory during cognitive tasks, providing valuable insights into how musical characteristics influence cognitive performance. Similarly, Sharma et al.~\cite{sharma2022impact}(2022) conducted a study examining the impact of various types of music on productivity and task performance, shedding light on the differential effects of instrumental and lyrical music on cognitive function.

\subsection{Eye Tracking}
In addition to the aforementioned studies, an innovative approach to eye-tracking technology was presented by~\cite{Malaikar2018Arduino}Malaikar et al. (2018) in their work titled "Arduino Based Eye-Writer Using PS3 Eye Camera." This research introduced an eye-tracking device and custom software, known as the Eye-Writer, which aimed to aid individuals with neuromuscular disorders and injuries in drawing or writing using only their eye movements. The Eye-Writer utilized an Arduino platform and a PS3 Eye Camera to track the movement of the user's eyes, enabling creative expression without the need for physical mobility. This novel application of eye-tracking technology showcases the diverse range of potential applications in assistive technology and human-computer interaction.

@@

\section{Conclusion and Future Works}
In conclusion, our study investigated the influence of auditory stimuli on eye movements using an eyetracking device. While the typing test results were not statistically significant, our analysis of the heatmap data revealed intriguing patterns in participants' eye movements under different auditory conditions. Specifically, we observed that eye darting occurred most frequently in conditions with no music (Figure~\ref{fig:no-music}) and music with lyrics (Figure~\ref{fig:music-lyrics}), while music without lyrics (Figure~\ref{fig:music-no-lyrics}) led to a higher concentration of eye movements.
Looking ahead, there are several avenues for future research and improvements. Firstly, it would be beneficial to incorporate a recording of the specific typing test completed by each participant, as we suspect that familiarity with certain song lyrics may have influenced typing performance. Additionally, expanding the length and diversity of text in the typing test could provide further insights into how different stimuli affect typing accuracy and speed. Experimenting with a broader range of auditory stimuli, including older songs or entirely different texts, could help elucidate the factors influencing participants' eye movements.
Furthermore, exploring the cognitive mechanisms underlying the observed eye movement patterns and their relationship with auditory processing could enhance our understanding of multimodal perception and attention. Investigating individual differences in response to auditory stimuli, such as musical preferences or language proficiency, could also offer valuable insights into the variability of eye movement behavior across diverse populations.
In summary, our findings contribute to the growing body of research on the interplay between auditory stimuli and visual attention, highlighting the need for continued exploration and refinement of experimental methodologies to uncover the underlying mechanisms. By addressing these avenues for future research, we can further advance our understanding of human perception and enhance the design of technologies aimed at optimizing cognitive performance in various contexts.

\begin{figure}
    \centering
    \includegraphics[width=0.5\linewidth]{1.png}
    \caption{Music with no Lyrics}
    \label{fig:music-no-lyrics}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[width=0.5\linewidth]{Music with Lyrics.png}
    \caption{Music with Lyrics}
    \label{fig:music-lyrics}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[width=0.5\linewidth]{3.png}
    \caption{No Music}
    \label{fig:no-music}
\end{figure}
